More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-11-29 2016-Weak-FH-Bisim/WeakBisim.tex
lemma 5

We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
\begin{enumerate}
\item For  $\symb{OT}$ in the form: 
$P[Q]_{j_0}	\models		\openrule
    {
       \set{\beta}_p,\Pred_p,\Post_p   }
         {\ostate{s_p} \OTarrow {\tau} \ostate{s^1_{p+1}}}$ \\
We obtain:\\
$P\models{\openrule
			{
				(\beta_{p})_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred_p}\!\!',  
				{\Post_p}\!\!'}
			{\ostate{(s_{p})_l^{l\in L\setminus L_Q}} \OTarrow {\tau}
				\ostate{({s}_{p}')_l^{l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
		%\[
		Q\models{\openrule
			{
				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {\Pred_p''},  
				{\Post_p''}}
			{\ostate{(s_{p})_l^{l\in L_Q}} \OTarrow {\alpha_p}
				\ostate{({s_{(p+1)}})_l^{l\in L_Q}}}
		}%\]
		$\\
and  $\Pred_p \iff {\Pred_p}\!\!'
		\land {\Pred_p}\!\!''\land \alpha_p=\beta_{pj_0}$, $\Post_p={\Post_p}\!\!'\uplus 
		{\Post_p}\!\!''$ where ${\Post_p''}$ is the restriction of $\Post_p$ over variables of $\Leaves(Q)$.
\item For $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
         {
           \set{\beta},\Pred,\Post }
         {\ostate{s} \OTarrow {\alpha} \ostate{s'}}$\\
We obtain:\\
$
		P\models{\openrule
			{
				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred}\,',  
				{\Post}\,'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
		%\[
		Q\models{\openrule
			{
				\beta_j^{j\in J\cap\Holes(Q)}, {\Pred}\,'',  
				{\Post}\,''}
			{\ostate{s_l^{l\in L_Q}} \OTarrow {\alpha'}
				\ostate{s_l'^{\,l\in L_Q}}}
		}%\]
		$
		and  $\Pred \iff {\Pred}\,'
		\land {\Pred}\,''\land \alpha'=\beta_{j_0}$, $\Post={\Post}\,'\uplus 
		{\Post}\,''$ where ${\Post}\,''$ is the restriction of $\Post$ over variables of $\Leaves(Q)$.

@@

\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
\end{mathpar}

@@

Considering the set of $\symb{OT}_p$ of $Q$ such that $p \in [0\ldots m+n+1]$, at each time a single open transition moves.   So we have for each open transition:

@@

By definition \ref{def:buildweakOT} we can conclude that we have for all $p\in[0\ldots n+m]$:

@@

Where $J_p = J\cap\Holes(Q)$, ???? $\gamma_{pj}=\vis{\beta_{pj}}$,\\  $\Pred \iff \Pred\,'
		\land \displaystyle{\bigvee_{p=0}^n}(\alpha_p= \beta_{pj_0}\land \Pred_p), \text{and~}
\Post=\Post\,'\uplus\biguplus_{p=0}^n
		\Post_p$

>>>>

We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
\begin{enumerate}
\item For  $\symb{OT}$ in the form: 
$P[Q]_{j_0}	\models		\openrule
    {
       \set{\beta}_p,\Pred_p,\Post_p   }
         {\ostate{s_p} \OTarrow {\tau} \ostate{s^1_{p+1}}}$ \\
We obtain:\\
$P\models{\openrule
			{
				(\beta_{p})_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred_p}\!\!',  
				{\Post_p}\!\!'}
			{\ostate{(s_{p})_l^{l\in L\setminus L_Q}} \OTarrow {\tau}
				\ostate{({s}_{p}')_l^{l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
		%\[
		Q\models{\openrule
			{
				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {\Pred_p''},  
				{\Post_p''}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}%\]
		$\\
and  $\Pred_p \iff {\Pred_p}\!\!'
		\land {\Pred_p}\!\!''\land \alpha_p=\beta_{pj_0}$, $\Post_p={\Post_p}\!\!'\uplus 
		{\Post_p}\!\!''$ where ${\Post_p''}$ is the restriction of $\Post_p$ over variables of $\Leaves(Q)$.
\item For $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
         {
           \set{\beta},\Pred,\Post }
         {\ostate{s} \OTarrow {\alpha} \ostate{s'}}$\\
We obtain:\\
$
		P\models{\openrule
			{
				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred}\,',  
				{\Post}\,'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
		%\[
		Q\models{\openrule
			{
				\beta_j^{j\in J\cap\Holes(Q)}, {\Pred}\,'',  
				{\Post}\,''}
			{\ostate{s_l^{l\in L_Q}} \OTarrow {\alpha'}
				\ostate{s_l'^{\,l\in L_Q}}}
		}%\]
		$
		and  $\Pred \iff {\Pred}\,'
		\land {\Pred}\,''\land \alpha'=\beta_{j_0}$, $\Post={\Post}\,'\uplus 
		{\Post}\,''$ where ${\Post}\,''$ is the restriction of $\Post$ over variables of $\Leaves(Q)$.

@@

\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}

@@

Considering the set of $\symb{OT}_p$ of $Q$ such that $p \in S$ and $S \subseteq [0\ldots m+n+1]$, at each time a single open transition moves.   So we have for each open transition:

@@

By definition \ref{def:buildweakOT} we can conclude that we have for all $p\in S$:

@@

Where\\ $\displaystyle{\bigcup_{p=0}^nJ_{p}} = J\cap\Holes(Q)$, $\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}}$, $\forall l\in L_Q,\, s_{0l}=s_l$, $s_{(n+1)l}=s'_l$  \\
  $\Pred \iff \Pred\,'
		\land \displaystyle{\bigvee_{p=0}^n}(\alpha_p= \beta_{pj_0}\land \Pred_p), \text{and~}
\Post=\Post\,'\uplus\biguplus_{p=0}^n
		\Post_p \quad$

\TODO{We will discuss quantif.}
